\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Update the discussion of UCT data to reflect the new values' interesting points

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network. Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs. On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.

Another point of particular interest is the very low ping and hop counts that appear in test case 2. The results show the test machine's IP as the IP that the content was being retrieved from. This is most likely a bug in our tool's parsing of tcpdump's output.

>>>>

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs. On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a bitrate far below what the connection supports. On the run 2 the video has been cached and is delivered with a significantly higher throughput. What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the ping to the server that delivers it has not changed. This suggests that the cache considers it to be "hotter" because of the additional request for it, and serves it at a higher throughput.

Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos. This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
